### 2020-07-14 conclusion.tex
final comment edits

The unique phenomena in \glspl{MSR}
necessitate the development of new reactor safety analysis software.
This thesis presents the latest developments in Moltres, namely coupling its
existing neutron diffusion module to the incompressible Navier-Stokes module
in MOOSE, and developing a decay heat model for short-term transients. We
demonstrated and verified some of its current capabilities through a static
neutronics study, and a coupled neutronics/thermal-hydraulics safety analysis
of the \gls{MSFR} concept.

The neutronics study showed good agreement between Moltres and Serpent. With
the relevant group constant data from Serpent,
Moltres could accurately replicate the $k_{eff}$, $\beta$,
$\alpha_T$, and multi-group neutron flux results from Serpent. The
$k_{eff}$ estimates from Moltres were approximately 100 pcm higher for all
measurements between 800 K and 1400 K. This discrepancy is notably smaller
than the discrepancies observed in the neutron diffusion and SP3 models
developed in OpenFOAM \cite{aufiero_extended_2013}. The $\beta$ and $\alpha_T$
values from Moltres had 1.46\% and 0.265\% discrepancies, respectively, to
Serpent's results. Lastly, the normalized six-group neutron flux from Moltres
and Serpent were visually indistinguishable from each other. The journal
article that introduced Moltres \cite{lindsay_introduction_2018} verified its
neutron diffusion model for a two-group thermal-spectrum \gls{MSBR} model;
the results of this study extends code-to-code verification of Moltres'
neutron diffusion model with the six-group, fast-spectrum \gls{MSFR} model.

Although Moltres currently lacks a proper turbulence model, our simplifying
assumption for the turbulent viscosity $\mu_t$ yielded good results for most
of the \gls{MSFR}
steady-state and transient analyses. The steady-state temperature and velocity
distributions showed many similiarities in their shapes and magnitudes to the
Polimi and TUDelft model results \cite{fiorina_modelling_2014}. Our
uniform $\mu_t$ assumption accounted for the minor differences in the flow at
the top of the core and the loss of delayed neutrons to out-of-core emissions.
The results with the decay heat model showed a slight flattening of the
temperature distribution in the core that is in line with our expectations
given the diffusion and advection of the decay heat precursors.

The unprotected reactivity insertion and loss of heat sink results showed the
same trends Fiorina et al. observed in their Polimi and TUDelft models. The
small difference in the temperature reactivity coefficient accounted for the
small difference in the magnitude of the peaks in power output and average
core temperature increase. The differences between the pointwise heat
exchanger in Moltres and the volumetric heat exchanger in the other two
models required minor adjustments in the relationship between flow rate
$\dot{m}$ and the heat transfer coefficient $h$ from the original
Dittus-Boelter correlation for the pump-initiated transients. Assuming a
directly proportional relationship between $\mu_t$ and $\dot{m}$ yielded
results in good agreement with the other two models for the pump overspeed
transient. However, Moltres performed poorly in the loss of flow transient as
this work could not incorporate buoyancy-driven flow and its associated
effects on $\mu_t$.

Overall, we have demonstrated that Moltres can handle most of the case
studies that this thesis covered.

@@

Further research and development on Moltres should aim to rectify the issues
mentioned in this thesis. This work has highlighted three main avenues for
improvement. Firstly, proper 2D/3D heat exchanger implementation
would allow us to move away from the 1D outer loop system and towards a full
2D/3D closed loop. The biggest change is that users would be able to use
the Boussinesq approximation for buoyancy-driven flow capability in Moltres.
Buoyancy-driven flow is a critical component in loss of forced flow scenarios
and these scenarios in turn are important accident transients in reactor
safety analyses.

Secondly, Moltres would benefit from a proper turbulence model such as the
$k$-$\epsilon$ or $k$-$\omega$ turbulence models. Turbulence effects are
significant in \gls{MSR} designs with fast flow, and they inform optimization
studies for improving flow patterns and eliminating local hotspots in eddies.
Our work in this thesis, particularly for the loss of flow transient, shows
that simplifying assumptions for turbulence lead to erroneous results under
flow conditions that deviate significantly from steady state.

Lastly, a compressible Navier-Stokes model would be essential for modeling
compressible flow effects such as variable temperature-dependent density
changes following a large reactivity insertion and finite wave propagation
speeds in a fluid. The presence of bubbles in the core from the gas sparging
system increases fuel compressibility and enhances compressibility effects
\cite{cervi_development_2019}.

>>>>

Unique phenomena in \glspl{MSR} necessitate the development of new reactor
safety analysis software. This thesis presents the latest developments in
Moltres, namely coupling its existing neutron diffusion module to the
incompressible Navier-Stokes module in MOOSE and developing a decay heat model
for short-term transients. This work demonstrated and verified some of
Moltres' current capabilities through a static-model
neutronics study and a coupled neutronics/thermal-hydraulics safety analysis
of the \gls{MSFR} concept.

The neutronics study showed good agreement between Moltres and Serpent 2. With
the relevant group constant data from Serpent 2,
Moltres could accurately replicate the $k_{eff}$, $\beta$,
$\alpha_T$, and multi-group neutron flux results from Serpent 2. The
$k_{eff}$ estimates from Moltres were approximately 100 pcm higher for all
measurements between 800 K and 1400 K. This discrepancy is notably smaller
than the discrepancies observed in the neutron diffusion and SP3 models
developed in OpenFOAM \cite{aufiero_extended_2013}. The $\beta$ and $\alpha_T$
values from Moltres had 1.46\% and 0.265\% discrepancies, respectively, to
Serpent 2's results. Lastly, the normalized six-group neutron fluxes from
Moltres all had less than 1\% discrepancy compared with Serpent 2.
The results of this study extend
the code-to-code verification of Moltres'
neutron diffusion model with the six-group, fast-spectrum \gls{MSFR} model.

Although Moltres currently lacks a proper turbulence model, the uniform
turbulent viscosity $\mu_t$ approximation was accurate enough to reproduce
most of the expected results for the \gls{MSFR}
steady-state and transient analyses. The steady-state temperature and velocity
distributions showed many similiarities in their shapes and magnitudes to the
Polimi and TUDelft model results \cite{fiorina_modelling_2014}. The uniform
$\mu_t$ approximation was responsible for the minor differences in the flow at
the top of the core and the loss of delayed neutrons to out-of-core emissions.
The results with the decay heat model showed a slight flattening of the
temperature distribution in the core that is in line with our expectations
given the diffusion and advection of the decay heat precursors.

The unprotected reactivity insertion and loss of heat sink results showed the
same trends Fiorina et al. \cite{fiorina_modelling_2014} observed in their
Polimi and TUDelft models. The
small difference in the temperature reactivity coefficient accounted for the
small difference in the magnitude of the peaks in power output and average
core temperature increase. The differences between the pointwise heat
exchanger in Moltres and the volumetric heat exchanger in the other two
models required minor adjustments in the relationship between flow rate
$\dot{V}$ and the heat transfer coefficient $h$ from the original
Dittus-Boelter correlation for the pump-initiated transients. Assuming a
directly proportional relationship between $\mu_t$ and $\dot{V}$ yielded
results in good agreement with the other two models for the pump overspeed
transient. However, Moltres performed poorly in the loss of flow transient as
this work could not incorporate buoyancy-driven flow and its associated
effects on $\mu_t$.

@@

Further research and development on Moltres should aim to rectify the issues
mentioned in this thesis. This work has highlighted three main avenues for
improvement. Firstly, proper 2D/3D heat exchanger implementation
would allow us to move away from the 1D outer loop system and towards a full
2D/3D closed loop. If this were implemented, users would be able to use
the Boussinesq approximation for buoyancy-driven flow capability in Moltres.
Buoyancy-driven flow is a critical component in loss of forced flow scenarios
which are important to reactor safety analyses.

Secondly, Moltres would benefit from a proper turbulence model such as
$k$-$\epsilon$ \cite{jones_prediction_1972} or $k$-$\omega$
\cite{wilcox_turbulence_2006}. Turbulence effects are
significant in \gls{MSR} designs with fast flow and they inform optimization
studies for improving flow patterns and eliminating local hotspots in eddies.
The current work, particularly the loss of flow accident scenario, shows
that simplifying assumptions for turbulence lead to erroneous results under
flow conditions that deviate significantly from steady state.

Lastly, a compressible Navier-Stokes model would be essential for modeling
effects such as variable temperature-dependent density
changes following a large reactivity insertion and finite wave propagation
speeds in the salt. The presence of bubbles in the core from the gas sparging
system increases fuel compressibility and enhances compressibility effects
\cite{cervi_development_2019}.

### 2020-07-14 introduction.tex
final comment edits

This thesis demonstrates latest capabilities of Moltres
\cite{lindsay_introduction_2018}.
In particular, this thesis presents two more recent
developments in Moltres, namely fully integrating \gls{MOOSE}'s incompressible
Navier-Stokes module into Moltres, and introducing a
decay heat model.
The main objective of this thesis is to verify Moltres'
latest capabilities in modeling multiphysics, steady-state, and transient
behavior of fast-spectrum \glspl{MSR} through the study of the \gls{MSFR}
concept. Code-to-code verification is an important exercise in software
development for ensuring that the application produces accurate and reliable
results. This thesis covers the \gls{MSFR} concept mainly because it has been
studied extensively with readily available data in the literature to verify
our results against. The \gls{MSFR} design also features interesting flow
patterns that greatly affect the steady-state and transient behavior. This
present work will first present a verification of Moltres' \gls{MSFR}
diffusion neutronics against the Monte Carlo neutron tranport software
Serpent 2, followed by a verification of
the coupled neutronics/thermal-hydraulics steady-state and accident transient
results against results from the Polimi and TUDelft models published by
Fiorina et al. \cite{fiorina_modelling_2014}. The
secondary objective is to identify areas of improvement in Moltres for future
research.

>>>>

This thesis demonstrates latest capabilities of Moltres
\cite{lindsay_introduction_2018}.
In particular, this thesis presents two more recent
developments in Moltres, namely fully integrating \gls{MOOSE}'s incompressible
Navier-Stokes module into Moltres, and introducing a
decay heat model.
The main objective of this thesis is to verify Moltres'
latest capabilities in modeling multiphysics, steady-state, and transient
behavior of fast-spectrum \glspl{MSR} through the study of the \gls{MSFR}
concept. Code-to-code verification is an important exercise in software
development for ensuring that the application produces accurate and reliable
results. This thesis covers the \gls{MSFR} concept mainly because it has been
studied extensively with readily available data in the literature to verify
our results against. The \gls{MSFR} design also features interesting flow
patterns that greatly affect the steady-state and transient behavior. This
present work will first present a verification of Moltres' \gls{MSFR}
diffusion neutronics against the Monte Carlo neutron tranport software
Serpent 2, followed by a verification of
the coupled neutronics/thermal-hydraulics steady-state and accident transient
results against two sets of results published by
Fiorina et al. \cite{fiorina_modelling_2014}. The two sets of results arose
from a collaborative benchmarking exercise by researchers at Politecnico di
Milano and Technical University of Delft with two separate \gls{MSR}
simulation tools. Section \ref{sec:litrev} discusses these tools
in greater detail. The
secondary objective is to identify areas of improvement in Moltres for future
development.

### 2020-07-14 model.tex
final comment edits

Serpent 2 provides standard geometric surfaces (e.g. planes, cylinders, cones)
for defining reactor geometries. In this work, the reactor geometry is the
same axisymmetric \gls{MSFR} geometry from the paper by Fiorina et al.
\cite{fiorina_modelling_2014}, as shown in Fig. \ref{fig:msfrgeom}.

@@

The neutron flux calculations in the central core region are
performed using the standard formulations for the time-dependent multigroup
neutron diffusion equations and \gls{DNP} concentration equations as shown in
equations \ref{eq:neut} and \ref{eq:dnp}:
%
\begin{align}
    \frac{1}{v_g} \frac{\partial \phi_g}{\partial t} &= \nabla \cdot D_g
    \nabla \phi_g - \Sigma^r_g \phi_g +
    \sum^G_{g' \neq g} \Sigma^s_{g' \rightarrow g} \phi_{g'} + \chi^p_g
    \sum^G_{g'=1} (1-\beta) \nu \Sigma^f_{g'} \phi_{g'} + \chi^d_g \sum^I_i
    \lambda_i C_i, \label{eq:neut} \\
    \frac{\partial C_i}{\partial t} &= \beta_i \sum^G_{g'=1} \nu \Sigma^f_{g'}
    \phi_{g'} - \lambda_i C_i - \vec{u} \cdot \nabla C_i + \nabla \cdot
    K \nabla C_i, \label{eq:dnp} \\
    \intertext{where}
    v_g &= \text{average speed of neutrons in group $g$ [cm$\cdot$s$^{-1}$],} 
    \nonumber \\
    \phi_g &= \text{neutron flux in group $g$ [cm$^{-2}\cdot$s$^{-1}$],}
    \nonumber \\
    t &= \text{time [s],} \nonumber \\
    D_g &= \text{diffusion coefficient of neutrons in group $g$
    [cm$^2\cdot$s$^{-1}$],} \nonumber \\
    \Sigma^r_g &= \text{macroscopic cross section for removal of neutrons from
    group $g$ [cm$^{-1}$],} \nonumber \\
    \Sigma^s_{g' \rightarrow g} &= \text{macroscopic cross section of
    scattering from $g'$ to $g$ [cm$^{-1}$],} \nonumber \\
    \chi^p_g &= \text{prompt fission spectrum for neutrons in group $g$,}
    \nonumber \\
    G &= \text{total number of discrete neutron groups,} \nonumber \\
    \nu &= \text{average number of neutrons produced per fission,} \nonumber
    \\
    \Sigma^f_{g} &= \text{macroscopic fission cross section for neutron in
    group $g$ [cm$^{-1}$],} \nonumber \\
    \chi^d_g &= \text{delayed fission spectrum for neutrons in group $g$,}
    \nonumber \\
    I &= \text{total number of delayed neutron precursor groups,} \nonumber \\
    \beta &= \text{total delayed neutron fraction,} \nonumber \\
    \beta_i &= \text{delayed neutron fraction of precursor group $i$,}
    \nonumber \\
    \lambda_i &= \text{average decay constant of delayed neutron precursors in
    precursor group $i$ [s$^{-1}$],} \nonumber \\
    C_i &= \text{concentration of delayed neutron precursors in precursor
    group $i$ [cm$^{-3}$],} \nonumber \\
    K &= \text{turbulent diffusion of the delayed neutron precursors
    [cm$^2\cdot$s$^{-1}$].} \nonumber
\end{align}
%

@@

A parabolic flow profile was imposed on the inlet Dirichlet boundary
condition. The equation for $u_x$ at the inlet is:
%
\begin{align}
    u_x &= -\xi \Big[\frac{y}{h} - \Big(\frac{y}{h}\Big)^2 
    \Big] \\
    \intertext{where}
    \xi &= \text{normalizing constant [m$\cdot$s$^{-1}$],} \nonumber \\
    y &= \text{height along the inlet [m],} \nonumber \\
    h &= \text{total height of the inlet $= 0.1875$ m.} \nonumber
\end{align}
%
$\xi$ is a normalizing constant that depends on the total volumetric flow
rate, $\dot{V}$. Solving the following set of equations in $v$ and $\dot{V}$:
%
\begin{align}
    v &= \xi [\frac{y}{h} - \frac{y^2}{h^2}] \\
    \dot{V} &= \int^h_0 \int^{2 \pi}_0 v r d\theta dy \\
    \intertext{where}
    r &= \text{radius [m],} \nonumber \\
    \theta &= \text{azimuthal angle [rad],} \nonumber
\end{align}
%
gives $\xi = 20.3401$ m$\cdot$s$^{-1}$ for $\dot{V} = 4.5$ m$^3\cdot$s$^{-1}$.

>>>>

Serpent 2 provides standard geometric surfaces (e.g. planes, cylinders, cones)
for defining reactor geometries. In this work, the reactor geometry uses the
same axisymmetric \gls{MSFR} geometry as the Polimi and TUDelft models
\cite{fiorina_modelling_2014}, as shown in Fig. \ref{fig:msfrgeom}.

@@

The neutron flux calculations in the central core region are
performed using the standard formulations for the time-dependent multigroup
neutron diffusion equations and \gls{DNP} concentration equations as shown in
equations \ref{eq:neut} and \ref{eq:dnp}:
%
\begin{align}
    \frac{1}{v_g} \frac{\partial \phi_g}{\partial t} &= \nabla \cdot D_g
    \nabla \phi_g - \Sigma^r_g \phi_g +
    \sum^G_{g' \neq g} \Sigma^s_{g' \rightarrow g} \phi_{g'} + \chi^p_g
    \sum^G_{g'=1} (1-\beta) \nu \Sigma^f_{g'} \phi_{g'} + \chi^d_g \sum^I_i
    \lambda_i C_i, \label{eq:neut} \\
    \frac{\partial C_i}{\partial t} &= \beta_i \sum^G_{g'=1} \nu \Sigma^f_{g'}
    \phi_{g'} - \lambda_i C_i - \vec{u} \cdot \nabla C_i + \nabla \cdot
    K \nabla C_i, \label{eq:dnp} \\
    \intertext{where}
    v_g &= \text{average speed of neutrons in group $g$ [cm$\cdot$s$^{-1}$],} 
    \nonumber \\
    \phi_g &= \text{neutron flux in group $g$ [cm$^{-2}\cdot$s$^{-1}$],}
    \nonumber \\
    t &= \text{time [s],} \nonumber \\
    D_g &= \text{diffusion coefficient of neutrons in group $g$
    [cm$^2\cdot$s$^{-1}$],} \nonumber \\
    \Sigma^r_g &= \text{macroscopic cross section for removal of neutrons from
    group $g$ [cm$^{-1}$],} \nonumber \\
    \Sigma^s_{g' \rightarrow g} &= \text{macroscopic cross section of
    scattering from $g'$ to $g$ [cm$^{-1}$],} \nonumber \\
    \chi^p_g &= \text{prompt fission spectrum for neutrons in group $g$,}
    \nonumber \\
    G &= \text{total number of discrete neutron groups,} \nonumber \\
    \nu &= \text{average number of neutrons produced per fission,} \nonumber
    \\
    \Sigma^f_{g} &= \text{macroscopic fission cross section for neutron in
    group $g$ [cm$^{-1}$],} \nonumber \\
    \chi^d_g &= \text{delayed fission spectrum for neutrons in group $g$,}
    \nonumber \\
    I &= \text{total number of delayed neutron precursor groups,} \nonumber \\
    \beta &= \text{total delayed neutron fraction,} \nonumber \\
    \beta_i &= \text{delayed neutron fraction of precursor group $i$,}
    \nonumber \\
    \lambda_i &= \text{average decay constant of delayed neutron precursors in
    precursor group $i$ [s$^{-1}$],} \nonumber \\
    C_i &= \text{concentration of delayed neutron precursors in precursor
    group $i$ [cm$^{-3}$],} \nonumber \\
    K &= \text{turbulent diffusion coefficient of the delayed neutron
    precursors [cm$^2\cdot$s$^{-1}$].} \nonumber
\end{align}
%

@@

A parabolic flow profile was imposed on the inlet Dirichlet boundary
condition. The equation for $u_x$ at the inlet is:
%
\begin{align}
    u_x &= -\xi \Big[\frac{y}{H} - \Big(\frac{y}{H}\Big)^2 
    \Big] \\
    \intertext{where}
    \xi &= \text{normalizing constant [m$\cdot$s$^{-1}$],} \nonumber \\
    y &= \text{height along the inlet [m],} \nonumber \\
    H &= \text{total height of the inlet $= 0.1875$ m.} \nonumber
\end{align}
%
$\xi$ is a normalizing constant that depends on the total volumetric flow
rate, $\dot{V}$. Solving the following set of equations in $v$ and $\dot{V}$:
%
\begin{align}
    v &= \xi [\frac{y}{H} - \frac{y^2}{H^2}] \\
    \dot{V} &= \int^h_0 \int^{2 \pi}_0 v r d\theta dy \\
    \intertext{where}
    r &= \text{radius [m],} \nonumber \\
    \theta &= \text{azimuthal angle [rad],} \nonumber
\end{align}
%
gives $\xi = 20.3401$ m$\cdot$s$^{-1}$ for $\dot{V} = 4.5$ m$^3\cdot$s$^{-1}$.

### 2020-07-14 msr.tex
final comment edits

\section{Literature Review of MSR Simulation Tools}

@@

Both DALTON and the COMSOL-based tool featured again in a later paper by
Fiorina et al.
\cite{fiorina_modelling_2014} in 2014 for a 2-D axisymmetric model of the
\gls{MSFR}. The authors compared \gls{MSFR} simulations results from both
tools, in which they dubbed the COMSOL and DALTON/HEAT tools the Polimi and
TUDelft models, respectively, after the universities where each tool was
developed. With multigroup
neutron diffusion and \gls{RANS} formulations on ultra fine meshes, both
models agreed on the steady-state neutron flux, temperature,
and \gls{DNP} distributions, as well as the power responses following various
accident transient initiations. Aufiero et al. \cite{aufiero_development_2014}
concurrently developed
a full-core 3-D model of the \gls{MSFR} in OpenFOAM, albeit with one-group
neutron diffusion to reduce computational load. With the 3-D model, the
authors could simulate the asymmetric reactor response to the failure of a
single pump in the sixteen-pump \gls{MSFR} configuration. Aufiero et al. also
provided quantitative data supporting the use of implicit coupling over
explicit coupling to obtain accurate solutions of the transient cases.

Separately, Zhang et al. \cite{zhang_couple_2014} introduced another
self-contained \gls{MSR} simulation tool named COUPLE. Similar to the COMSOL
and OpenFOAM-based models, COUPLE solves the multigroup neutron diffusion
equations and the incompressible Navier-Stokes equations with the
$k$-$\epsilon$ turbulence model. The authors verified COUPLE's neutronics and
thermal-hydraulics against MCNP and a FLUENT-based model, respectively, before
presenting their multiphysics steady-state results with a 2-D axisymmetric
model of the \gls{MSFR}.

@@

The present work uses the same 2-D square-cylindrical \gls{MSFR} design to
compare our results to results published by Fiorina et al.
\cite{fiorina_modelling_2014}. The design is a 2-D axisymmetric representation
of the \gls{MSFR} with the sixteen individual external loops homogenized into
a single outer loop as shown in Figure \ref{fig:msfrgeom}. For the multigroup
group constants calculations in Serpent, the 2-D axisymmetric model is
extended into a 3-D model by a 360-degree rotation about the
central axis. The material definitions are the same as those specified in the
reference \gls{MSFR} model \cite{brovchenko_neutronic_2019}. Accordingly, the
pump and heat exchanger regions
are assumed to be composed of 100\% fuel salt. While this is an approximation,
the outer loop is shielded from the core by a layer of boron carbide and sees
sufficiently low neutron fluxes that we may neglect its exact neutronic
properties.
%
\begin{figure}[t!] 
	\centering
	\includegraphics[width=0.5\textwidth]{msfr-geom}
	\caption{2-D axisymmetric model of the \gls{MSFR} core used for the
	simulations in Serpent. All dimensions are in meters.
	\cite{brovchenko_neutronic_2019}}
	\label{fig:msfrgeom}
\end{figure}

>>>>

\section{Literature Review of MSR Simulation Tools} \label{sec:litrev}

@@

Both DALTON and the COMSOL-based tool featured again in a later paper by
Fiorina et al. \cite{fiorina_modelling_2014} in 2014 for a 2-D axisymmetric
model of the \gls{MSFR}. The authors, from Politecnico di Milano and
Technical University of Delft, compared \gls{MSFR} transient safety
analysis results from both tools. They referred to the COMSOL and DALTON/HEAT
\gls{MSFR} models as the Polimi and TUDelft models, respectively, after the
universities where each application was developed. This thesis also follows
this naming convention. With
multigroup neutron diffusion and \gls{RANS} formulations on ultra fine meshes,
both models agreed on the steady-state neutron flux, temperature,
and \gls{DNP} distributions, as well as the power responses following various
accident transient initiations.
Aufiero et al. \cite{aufiero_development_2014} concurrently developed
a full-core 3-D model of the \gls{MSFR} in OpenFOAM, albeit with one-group
neutron diffusion to reduce computational load. With the 3-D model, the
authors could simulate the asymmetric reactor response to the failure of a
single pump in the sixteen-pump \gls{MSFR} configuration. Aufiero et al. also
provided quantitative data supporting the use of implicit coupling over
explicit coupling to obtain accurate solutions of the transient cases.

Separately, Zhang et al. \cite{zhang_couple_2014} introduced another
self-contained \gls{MSR} simulation tool named COUPLE. Similar to the COMSOL
and OpenFOAM-based models, COUPLE solves the multigroup neutron diffusion
equations and the incompressible Navier-Stokes equations with the
$k$-$\epsilon$ turbulence model. The authors verified COUPLE's neutronics and
thermal-hydraulics against MCNP and a FLUENT-based model, respectively, and
presented their multiphysics steady-state results for a 2-D axisymmetric
model of the \gls{MSFR}.

@@

The present work uses the same 2-D square-cylindrical \gls{MSFR} design to
compare the present results to results from the Polimi and TUDelft models
\cite{fiorina_modelling_2014}. The design is a 2-D axisymmetric representation
of the \gls{MSFR} with the sixteen individual external loops homogenized into
a single outer loop as shown in Figure \ref{fig:msfrgeom}. For the multigroup
group constants calculations in Serpent, the 2-D axisymmetric model is
extended into a 3-D model by a 360-degree rotation about the
central axis. The material definitions are the same as those specified in the
reference \gls{MSFR} model \cite{brovchenko_neutronic_2019}. Accordingly, the
pump and heat exchanger regions
are assumed to be composed of 100\% fuel salt. While this is an approximation,
the outer loop is shielded from the core by a layer of boron carbide and sees
sufficiently low neutron fluxes that we may neglect its exact neutronic
properties.
%
\begin{figure}[t!] 
	\centering
	\includegraphics[width=0.5\textwidth]{msfr-geom}
	\caption{2-D axisymmetric model of the \gls{MSFR} core used for the
	simulations in Serpent. All dimensions are in meters.
	\cite{brovchenko_neutronic_2019}}
	\label{fig:msfrgeom}
\end{figure}
